### 2016-03-07 paper/icfp16-submission/semantics.tex
fixed genWitness

\begin{mcode}
genArgs :: $e$ -> [$v$]
genArgs $e$ = loop []
  where
  loop vs = case eval $\triple{\eapp{e}{vs}}{\emptysu}{\emptysu}$ of
             $\triple{\efun{x}{e}}{\vsu}{\tsu}$:_ -> loop ($\vhole{\thole}$ : vs)
                           -- $\ehole$, $\thole$ are fresh
             _          -> vs
\end{mcode}
\caption{Find number of arguments for target function}
\label{fig:algo-gen-args}
\end{figure}

@@

\begin{cor}{\textbf{[Witness Generation]}}
\label{thm:generation}
  If |genWitness k $e$ = $\ $ $\triple{\eapp{e}{v_1 \ldots v_n}}{\vsu}{\tsu}\ldots$|,
  then for all types $t_1 \ldots t_n$ there exist values $w_1 \ldots w_n$ such that
  $\steps{\eapp{e}{w_1 \ldots w_n}}{\emptysu}{\emptysu}{\stuck}{\vsu'}{\tsu'}$.
\end{cor}

>>>>

\begin{mcode}
genArgs :: $e$ -> [$v$]
genArgs $e$ = loop []
  where
  loop vs = case eval $\triple{\eapp{e}{vs}}{\emptysu}{\emptysu}$ of
             $\triple{\efun{x}{e}}{\vsu}{\tsu}$:_ -> loop ($\vhole{\thole}$ : vs)
                           -- $\ehole$, $\thole$ are fresh
             _          -> vs
\end{mcode}
\caption{Find number of arguments for target function\RJ{FIX FORMAT}}
\label{fig:algo-gen-args}
\end{figure}

@@

\begin{cor}{\textbf{[Witness Generation]}}
\label{thm:generation}
  If $$\genWitness{k}{e} = \triple{\eapp{e}{v_1 \ldots v_n}}{\vsu}{\tsu}\ldots$$
  then for all types $t_1 \ldots t_n$ there exist values $w_1 \ldots w_n$ such that
  $\steps{\eapp{e}{w_1 \ldots w_n}}{\emptysu}{\emptysu}{\stuck}{\vsu'}{\tsu'}$.
\end{cor}
